Lossy compression of DNA sequencing quality data

### 2015-04-07 manuscript/q-compression.tex
Added data sets.

%\usepackage{doi}

@@

\textit{TODO: MiSeq data set} \ldots

>>>>

%\usepackage{doi}
\usepackage{url}

@@

\textit{Escherichia coli} str. K-12 MG1655 MiSeq data was downloaded from \url{http://www.illumina.com/systems/miseq/scientific_data.html}, which are generated from a
fragment library (insert size of 180bp nt; 1,145,8940 paired-end reads). 
The corresponding reference sequence was obtained
from the NCBI RefSeq database (NC\_000913.2).
